Z-Resonance at LEP

### 2010-07-20 Z0-Publikation/tex/paper-template.tex
intro schon besser

@@

The Z$^0$-particle, which was supposed to be produced at LEP, can decay in
various ways. One of these possibilities is the decay via two different quarks 
(Z$^0→q\overline{q'}$), another one could be the decay via two charged leptons
like Z$^0→ μ^+μ^-$. The first one of the mentioned decays can be seen
as two jets which can be measured in hadronic calorimeters. The leptonic decay
is measured due to registration of leptons in electromagnetic calorimeters.

@@

The LEP is ....
The L3 detector consists of ...
.....
\section{ Data analysis}

For a detailed analysis of the mentioned processes it is important to be able
to distinguish between muonic and hadronic decays, we did some Monte Carlo
studies to figure out how these processes look like. This gave us the
possibility to apply cuts on the measured distributions.

>>>>

\usepackage{siunitx}
\usepackage[justification=raggedright,singlelinecheck=false]{caption}
\sisetup{
	seperr		=	true,
	trapambigerr	=	true,
	openerr		=	(,
	closeerr	=	),
	expproduct	=	cdot,
	padnumber	=	both,
	stickyper	=	true,
	per		=	slash,
	trapambigfrac	=	true,
	repeatunits	=	false,
	openfrac	=	(,
	closefrac	=	),
	prefixsymbolic 	=	true,
	prefixproduct	=	cdot,
	decimalsymbol	=	.,
        tabnumalign     =       left,
        tabtextalign    =       left
}

@@

LEP was designed to be able to deliver center of mass energies $\sqrt{s}$ from
some 89 up to \SI{209}{\giga\electronvolt}. This is enough to produce Z-bosons,
which should have a mass of about \SI{91}{\giga\electronvolt}, as it was
predicted by the standard model. Therefore the Z$^0$-particle was supposed to be
produced at LEP. It can decay in various ways, but always into pairs of one
fermion and one antifermion. One of these possibilities is the decay via two
different quarks (Z$^0→q\overline{q'}$), another one could be the decay via two
charged leptons like Z$^0→ μ^+μ^-$. The first one of the mentioned decays can be
seen as two jets which can be measured in hadronic calorimeters. The leptonic
decay is measured due to registration of leptons in electromagnetic
calorimeters. All of these layers have an almost cylindrical shape in order to
cover as much of the solid angle as possible. This is also the reason for the
installation of the endcaps.

@@

In our case the hadronic calorimeter and the muon chamber are the most
important parts. The hadronic calorimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without an important loss of energy, because these are the only particles that
are able to reach there. For further information about the detector design can
be found in \cite{script}.

\section{ Data analysis}

For a detailed analysis of the mentioned processes it is important to be able
to distinguish between muonic and hadronic decays, we did some Monte Carlo
studies to figure out how these two processes look like. This gave us the
possibility to apply cuts on the measured distributions. In this paper we are
already able to show the results of measurements at center of mass energies at
89.48, 91.33 and \SI{93.02}{\giga\electronvolt}.
